### 2024-03-28 tesis_Ashish/Chapter7/chapter7.tex
update 28 Mar

\begin{figure}[H]
  \centering
  \includegraphics[width=1 \columnwidth]{ashish_thesis/it_newgeometry_.png}
  \caption[Phase II CMS Inner Tracker]{ \onehalfspacing A layout of the CMS Phase II Inner Tracker showing four TEPX disks, eight TFPX disks and four TBPX layers \cite{Collaboration:275907420}.}
  \label{fig:Innertracker}
\end{figure}

@@

\item The CMS Tracker's Phase II upgrade includes the Timing Layer, equipped with Low Gain Avalanche Detectors (LGAD) to improve time measurement of charged particles. This enhancement helps distinguish particles from different vertices, reducing pileup in event reconstruction. LGADs, with their charge amplification capability, offer superior time resolution. Charged particles generate electron-hole pairs in the LGAD sensor, which are then amplified and collected quickly for improved timing accuracy. The system aims for a 30-40 picosecond time resolution, enhancing particle identification and handling pileup effects. Covering a pseudorapidity range of $|\eta|$ < 2.5, the Timing Layer has a lightweight, radiation-tolerant support structure with efficient cooling, ensuring reliable performance.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.7\columnwidth]{ashish_thesis/tepx_clusters_2.png}
  \caption[TEPX Cluster Map]{TEPX cluster map in the XY plane for pileup 200 simulated sample having 5000 events. %Map showing coordinates of TEPX clusters in CMS global coordinate system.
    It shows clusters in one TEPX disk consisting of 5 rings. Hot regions are showing the module overlap. %for all rings (red, orange, green, yellow). Number of x bins is 1000, x bins range from -40 to 40.
    x bin size is 0.1 mm and %Number of y bins is 1000, y bins range from -40 to 40.
    y bin size is 0.1 mm.}
  \label{fig:tepx_cl}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.7\columnwidth]{ashish_thesis/tepx_D4R!_clusters._allpu_1.png}
  \caption[D4R1 Clusters All Pileup]{Distribution of number of clusters for TEPX Disk 4 Ring 1 for all pileup samples.}
  \label{fig:tepx_cl_allPU}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{ashish_thesis/michigan_2.png}
  \caption[TEPX cluster linear fit per disk]{\onehalfspacing Left: Simulated mean number of clusters for TEPX disks as a function of pileup. A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200. Right: %Deviation from linearity for clusters for  TEPX disks. The non-linearity is calculated as
    The relative difference between the data points and the values of the fit function at the respective pileup value \cite{Collaboration:275907420}.}
  \label{fig:CMS_4205}
\end{figure}

@@

\begin{figure}[!htp]
\centering
\includegraphics[width=0.6\textwidth]{ashish_thesis/twofoldinphi.png}
\caption[Module Overlap Two Fold Coincidences in phi]{%                                                                                                                                     
  Example of module overlap between same ring modules that can give rise to two fold coincidences in phi.
}
\label{fig:cluster_ring_4000}
\end{figure}

@@

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/dr_dphi_variables1_1.png}
\caption[New Variables For Two Fold Coincidences]{%
  r, $\phi$ variables used to define coincidence clusters. %These variables take into account track angle and curvature.
}
\label{fig:drdphi_diagram}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/D4R1_S2_drdphi_cut_2.png}
\caption[Pileup 0.5 Cluster Count in D4R1 vs. dr & d$\phi$]{%
  Distribution of cluster count as a function of dr and d$\phi$ variables for pileup 0.5 for Disk 4 Ring 1. The black curve represents the total two-fold coincidence counts, the red curve depicts the true two-fold coincidence counts, and the green curve indicates the fake two-fold coincidence counts.
}
\label{fig:cluster_dr_dphi_dist}
\end{figure}

@@

\begin{figure}[!htp]
\centering
\includegraphics[width=0.3\textwidth]{ashish_thesis/twofoldinr_exam.png}
\caption[Examples of two fold coincidences in r]{%                                                                                                                                                       
  Definition of two-fold coincidences in r from the module overlap regions.
}
\label{fig:cluster_ring_72034}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.7\columnwidth]{ashish_thesis/tepx_D4R1_coin_allpu_1.png}
  \caption[TEPX D4R1 Two-Fold Coincidences All Pileup]{Distribution of number of two-fold coincidences for TEPX Disk 4 Ring 1 for all pileup values \cite{Collaboration:275907420}.}
  \label{fig:tepx_coin_allPU}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{ashish_thesis/michigan_4.png}
  \caption[TEPX two-fold coincidences linear fit for Disk 4 Ring 1]{\onehalfspacing Left: Simulated mean number of two-fold coincidences in phi for TEPX Disk 4 Ring 1 as a function of pileup. A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200. Right: The relative difference between the data points and the values of the fit function at the respective pileup value \cite{Collaboration:275907420}.}
  \label{fig:CMS_4207}
\end{figure}

@@

\newpage
\begin{figure}[H]
  \centering
  \includegraphics[width=0.7\columnwidth]{ashish_thesis/tepx_threefold_allpu.png}
  \caption[TEPX Disk 4 Ring 2 Three Fold Coincidences]{Distribution of number of three fold coincidences for TEPX Disk 4 Ring 2 for all pileup values.}
  \label{fig:tepx_3foldcoin_allPU_2}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{ashish_thesis/TEPX_threefold_linearity.png}
  \caption[Disk 4 all rings Three-Fold Coincidences Linearity]{Left: Simulated mean number of three-fold coincidences for all Disk 4 rings as a function
    of pileup. Right: Deviation from linearity for Disk 4 all rings, the relative difference between the data points and the values of the fit function at the respective pileup value.}
  \label{fig:tepx_3foldcoin_allPU_3}
\end{figure}

>>>>

\begin{figure}[H]
  \centering
  \includegraphics[width=1 \columnwidth]{ashish_thesis/it_newgeometry_.png}
  \caption[Phase 2 CMS inner tracker]{ \onehalfspacing A layout of the CMS Phase II Inner Tracker showing four TEPX disks, eight TFPX disks and four TBPX layers \cite{Collaboration:275907420}.}
  \label{fig:Innertracker}
\end{figure}

@@

\item The CMS Tracker Phase II upgrade includes the Timing Layer, equipped with Low Gain Avalanche Detectors (LGAD) to improve time measurement of charged particles. This enhancement helps distinguish particles from different vertices, reducing pileup in event reconstruction. LGADs, with their charge amplification capability, offer superior time resolution. Charged particles generate electron-hole pairs in the LGAD sensor, which are then amplified and collected quickly for improved timing accuracy. The system aims for a 30-40 picosecond time resolution, enhancing particle identification and handling pileup effects. Covering a pseudorapidity range of $|\eta|$ < 2.5, the Timing Layer has a lightweight, radiation-tolerant support structure with efficient cooling, ensuring reliable performance.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.7\columnwidth]{ashish_thesis/tepx_clusters_2.png}
  \caption[TEPX cluster map]{TEPX cluster map in the XY plane for pileup 200 simulated sample having 5000 events. %Map showing coordinates of TEPX clusters in CMS global coordinate system.
    It shows clusters in one TEPX disk consisting of 5 rings. Hot regions are showing the module overlap. %for all rings (red, orange, green, yellow). Number of x bins is 1000, x bins range from -40 to 40.
    x bin size is 0.1 mm and %Number of y bins is 1000, y bins range from -40 to 40.
    y bin size is 0.1 mm.}
  \label{fig:tepx_cl}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.7\columnwidth]{ashish_thesis/tepx_D4R!_clusters._allpu_1.png}
  \caption[D4R1 clusters all pileup]{Distribution of number of clusters for TEPX Disk 4 Ring 1 for all pileup samples.}
  \label{fig:tepx_cl_allPU}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{ashish_thesis/michigan_2.png}
  \caption[TEPX clusters linear fit per disk]{\onehalfspacing Left: Simulated mean number of clusters for TEPX disks as a function of pileup. A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200. Right: %Deviation from linearity for clusters for  TEPX disks. The non-linearity is calculated as
    The relative difference between the data points and the values of the fit function at the respective pileup value \cite{Collaboration:275907420}.}
  \label{fig:CMS_4205}
\end{figure}

@@

\begin{figure}[!htp]
\centering
\includegraphics[width=0.6\textwidth]{ashish_thesis/twofoldinphi.png}
\caption[Module Overlap two-fold coincidences in phi]{%                                                                                                                                     
  Example of module overlap between same ring modules that can give rise to two fold coincidences in phi.
}
\label{fig:cluster_ring_4000}
\end{figure}

@@

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/dr_dphi_variables1_1.png}
\caption[New variables for two-fold coincidences]{%
  r, $\phi$ variables used to define coincidence clusters. %These variables take into account track angle and curvature.
}
\label{fig:drdphi_diagram}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/D4R1_S2_drdphi_cut_2.png}
\caption[Pileup 0.5 cluster count in D4R1 vs. dr and d$\phi$]{%
  Distribution of cluster count as a function of dr and d$\phi$ variables for pileup 0.5 for Disk 4 Ring 1. The black curve represents the total two-fold coincidence counts, the red curve depicts the true two-fold coincidence counts, and the green curve indicates the fake two-fold coincidence counts.
}
\label{fig:cluster_dr_dphi_dist}
\end{figure}

@@

\begin{figure}[!htp]
\centering
\includegraphics[width=0.3\textwidth]{ashish_thesis/twofoldinr_exam.png}
\caption[Examples of two-fold coincidences in r]{%                                                                                                                                                       
  Definition of two-fold coincidences in r from the module overlap regions.
}
\label{fig:cluster_ring_72034}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.7\columnwidth]{ashish_thesis/tepx_D4R1_coin_allpu_1.png}
  \caption[TEPX D4R1 two-fold coincidences all pileup]{Distribution of number of two-fold coincidences for TEPX Disk 4 Ring 1 for all pileup values \cite{Collaboration:275907420}.}
  \label{fig:tepx_coin_allPU}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{ashish_thesis/michigan_4.png}
  \caption[TEPX two-fold coincidences linear fit for Disk 4 Ring 1]{\onehalfspacing Left: Simulated mean number of two-fold coincidences in $\phi$ for TEPX Disk 4 Ring 1 as a function of pileup. A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200. Right: The relative difference between the data points and the values of the fit function at the respective pileup value \cite{Collaboration:275907420}.}
  \label{fig:CMS_4207}
\end{figure}

@@

\newpage
\begin{figure}[H]
  \centering
  \includegraphics[width=0.7\columnwidth]{ashish_thesis/tepx_threefold_allpu.png}
  \caption[TEPX Disk 4 Ring 2 three-fold coincidences]{Distribution of number of three fold coincidences for TEPX Disk 4 Ring 2 for all pileup values.}
  \label{fig:tepx_3foldcoin_allPU_2}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{ashish_thesis/TEPX_threefold_linearity.png}
  \caption[Disk 4 all rings three-fold coincidences linearity]{Left: Simulated mean number of three-fold coincidences for all Disk 4 rings as a function
    of pileup. Right: Deviation from linearity for Disk 4 all rings, the relative difference between the data points and the values of the fit function at the respective pileup value.}
  \label{fig:tepx_3foldcoin_allPU_3}
\end{figure}
